Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

\paragraph{Amplifying groups for boundary cases.} Recall in our
3-level policy, the medium gap case (Lemma \ref{3levelmedium}) is the
boundary case when the gap $|\mu_1-\mu_2|$ is
$\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and
$O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is
not large enough to conclude that with high probability agents in both
the second level and the third level all pull the best arm. The gap is
also not small enough to conclude that with high probability both arms
are explored enough times in the second level. We need to worry about
the situation in which the sub-optimal arm does not get pulled enough
times in the first two levels and some agents in the third level may
pull the sub-optimal arm. Such situation is naturally ruled out in our
3-level policy for the following reason. Agents in the third level
observe the history of the entire first level while agents in the
second level only observes the history of a single first-level
group. For each arm, even if it is not explored enough times in the
second level, its empirical mean concentrates closer to its actual
mean in the history observed by a third-level agent than the one
observed by a second-level agent. Therefore, although the gap in the
medium gap case is just not large enough for agents in the second
level to all pull the best arm, it is large enough for agents in the
third level to all pull the best arm.

>>>>

\paragraph{Amplifying groups for boundary cases.} Recall in the
three-level policy, the medium gap case (Lemma \ref{3levelmedium})
corresponds to the case where the gap $\Delta$ is between
$\Omega\left({{1}/{T_1}}\right)$ and
$O\left(\sqrt{{\log(T)}/{T_1}}\right)$. This is a boundary case since
$\Delta$ is neither large enough to conclude that with high
probability agents in both the second level and the third level all
pull the best arm, nor small enough to conclude that both arms are
explored enough times in the second level (due to
anti-concentration). In this case, we need to ensure that agents in
the third level can eliminate the inferior arm. This issue is easily
resolved in the three-level policy since the agents in the third level
observe the history of the entire first level, which provides
sufficiently accurate reward estimates for both arms.

\OMIT{about the situation in which the sub-optimal arm does not get
  pulled enough times in the first two levels and some agents in the
  third level may pull the sub-optimal arm.  Such situation is
  naturally ruled out in our 3-level policy for the following
  reason. Agents in the third level observe the history of the entire
  first level while agents in the second level only observes the
  history of a single first-level group. For each arm, even if it is
  not explored enough times in the second level, its empirical mean
  concentrates closer to its actual mean in the history observed by a
  third-level agent than the one observed by a second-level
  agent. Therefore, although the gap in the medium gap case is just
  not large enough for agents in the second level to all pull the best
  arm, it is large enough for agents in the third level to all pull
  the best arm.}
